Vienna Elections 2020: Analysis of parties' ads on facebook

### 2021-01-06 _post/2020-12-19-vienna-elections-2020-analysis-of-parties-ads-on-facebook/welcome.Rmd
changed post directory; applied ful site.yml

write_rds(df_ads_all, path=paste0(wdr,"/data/scraped_ads",time_stamp,".rds"))
```

@@

```{r include=FALSE}
df_ads <- readr::read_rds(file=here::here("blog_data", 
                                          "vienna_elections_2020_facebook",
                                          "df_ads.rds")) 
```

@@

```{r include=FALSE}
pages_of_interest <- readxl::read_xlsx(path=here::here("blog_data", "vienna_elections_2020_facebook", "df_pages_of_interest.xlsx")) %>% 
  # filter(include=="yes") %>% 
  distinct(page_name, party, page_type, include) %>% 
  mutate(party=stringr::str_to_upper(party, locale="de"))
```

@@

readr::write_csv2(df_impression_check,file=here::here("blog_data","vienna_elections_2020_facebook","df_impression_check.csv"))
```

>>>>

#write_rds(df_ads_all, path=paste0(wdr,"/data/scraped_ads",time_stamp,".rds"))
```

@@

```{r include=FALSE}
df_ads <- readr::read_rds(file=here::here("_blog_data", 
                                          "vienna_elections_2020_facebook",
                                          "df_ads.rds")) 
```

@@

```{r include=FALSE}
pages_of_interest <- readxl::read_xlsx(path=here::here("_blog_data", "vienna_elections_2020_facebook", "df_pages_of_interest.xlsx")) %>% 
  # filter(include=="yes") %>% 
  distinct(page_name, party, page_type, include) %>% 
  mutate(party=stringr::str_to_upper(party, locale="de"))
```

@@

#readr::write_csv2(df_impression_check,file=here::here("blog_data","vienna_elections_2020_facebook","df_impression_check.csv"))
```
